---
title: "The Evolution of U.S. Book Retailer Sales 1992-2022"
author: "Emilio Avalos, Jaime Fastino, Nicole Romangsuriat"
date: "05/01/2023"
output: rmarkdown::github_document
---

```{r setup, echo=FALSE, include=FALSE}
library(fpp2)
df = read.csv("Book Retailer Data.csv")
```
## Introduction

In this document we will be analyzing the monthly retail sales of bookstores in the United states from January 1992 to December 2022. Given the technological innovations that have popularized kindle and other e-reading platforms over the past years, we would like to investigate how book retailer sales have been impacted. We hypothesize that the emergence of bookstore alternatives such as e-book reading platforms (eg. Kindle and Wattpad) and digital comic platforms (eg. Webtoon) in the 2010s have caused brick-and-mortar bookstore sales to dwindle in recent years. However we are taking this analysis further back by exploring bookstore sales from 1992 to 2022, to see how factors such as increases in technological advancements, education access, and U.S. literacy rates, have influenced book retail store sales within these two decades.

We will start by generating a time series plot and conducting qualitative analysis to investigate topics such as trend, cyclic behavior, and seasonality. In the second part of the analysis, we will investigate various models including baseline models, time series decomposition, exponential smoothing, the SARIMA family, linear regression, and non-linear models. After this investigation, we will then compare in-sample accuracies to determine which model has the best fit.

## About the Data Set

We are utilizing data from the U.S. Census Bureau website, particularly from the "Retail Food and Services Sales" dataset. The U.S. Census Bureau had collected this data from the Monthly Retail Trade Survey, Annual Retail Trade Survey, Service Annual Survey, and national administrative records. This dataset provides monthly sales data from 1992 to 2022 for each type of store under this category, including data for bookstore sales. We pulled this data and compiled it into a separate dataset with 372 data values. 

## U.S. Monthly Bookstore Sales Time Series Plot

```{r, echo=FALSE, fig.align='center', out.width='80%'}

BookSales = ts(df$Sales, start = 1992, frequency = 12)

fig1 = autoplot(BookSales, color="purple") + ggtitle("US Monthly Bookstore Sales (1992-2022)") + xlab("Year") + ylab("Sales ($ millions)") + theme(plot.title = element_text(hjust = 0.5))

print(fig1)
```

## Qualitative Analysis

By doing an initial assessment of this time series graph, its properties can be summarized as follows:

- **Trend:** A non-constant trend is evident in this dataset. The data appears to increase from 1992 to around 2008, illustrating a vast increase in bookstore retail sales during this time period. The end of the 1990s and the start of the new millennium was the world had entered into a global Information Age, in which nation-wide education levels had increased with greater funding in U.S. public schools, post-secondary level tuition grants, and advancements in formal education (National Archives and Records Administration). This is likely attributed to the increase in education rates and literacy rates, hence increasing the portion of the population who purchases books from book retailers. Data levels decrease slowly from around 2008 to 2020. This is likely attributed to the increase in e-book platforms at the time. Sony had released its first e-reader in 2006 while Amazon had launched its kindle in 2007 (Atwell, 2023). These devices became popular around 2008 as more people started using it in lieu of going to the bookstore and picking a paperback copy off the shelves. E-books can be preferable as they are less expensive, can fit into any device as long as there is enough storage, and does not require physical space or carry any weight in your bag. Other e-reading platforms such as Wattpad, an online platform in which writers can publish and share their own stories, as well as alternatives such as audiobooks and digital graphic comic apps have also started to increase in popularity, driving customers away from the traditional brick-and-mortar bookstore. The data suddenly drops in 2020, likely due to the COVID pandemic and subsequent lockdowns that prevent people from stepping outside their homes into public places, causing bookstore sales to plummet. The data then slowly increases as the pandemic ends, illustrating people visiting bookstores once more. This continues until the end of 2022, which could be because of the current trend of buying secondhand books from local mom-and-pop stores. There was and currently is a trend of buying secondhand products as a way to decrease waste and be more environmentally conscious. This has extended to increasing the shelf life of books, as demonstrated by a 5.5% increase in the secondhand book industry in 2022 alone (Talbot, 2022).   

- **Level:** There is a non-constant level that is evident in the dataset. From 1992 to roughly 2008, the data level increases gradually from \$750 million to \$1.75 billion, as U.S. education levels and literacy rates rise. It then decreases to roughly \$775 million until around 2020, as e-readers and online book platforms and alternatives are popularized, before dropping to roughly \$200 million as the pandemic causes brick-and-mortar bookstores to close. The data level finally increases gradually once more to roughly \$900 million as purchasing secondhand books are becoming a trend. 

- **Cyclical Behaviour:** There appears to be little cyclic behaviour present in the dataset. There is little to no irregular data level variation, as most if not all of the fluctuations appear to occur in a repeating pattern in the time series plot.

- **Outliers:** There is an outlier present in 2020. During this time, there is a sharp drop in data values from \$1 billion in February 2020 to \$200 million in March 2020 that is likely because of the COVID-19 pandemic panic. The month of March had started what most people associate with the start of COVID in the U.S., when the pandemic has taken its turn for the worst and had resulted in subsequent lockdowns and quarantine procedures. Around this time, people were not leaving their houses and therefore not going to birkc-and-mortar book stores which caused sales to drop. We can see an increase in data levels for the next coming months as retail stores start to open and people become more comfortable with going outside into public places again.  

- **Seasonality:** There is significant seasonality evident in the dataset, specifically annual seasonality. There are giant data fluctuations from roughly hundreds of millions of dollars to billions of dollars that seem to occur on a yearly basis. For each data fluctuation that happens per year, it looks like there are 2 specific spikes in data. From 1992 to 2000, the latter spike is almost twice the size of the first spike. From 2000 to 2008, these two spikes reach roughly similar peaks, and from 2008 until the end of 2022, the latter spike is either slightly higher than the first or is roughyl the same. The first spike could be because of the spring semester or quarter start dates of schools and universities throughout the nation, that cause tens of millions of students to go book retailers for "back-to-school" supplies such as textbooks, notebooks, literary works for assignments, stationary, and more. As most schools in the U.S. have similar start dates in the spring sometime in January, this likely caused an drastic increase in book retailer sales. The second spike could also be attributed to "back-to-school season" for the fall semester. Most U.S. schools and academic institutions start their fall semesters in late August or mid September, likely causing a sudden spike in bookstore visits and subsequent retail sales. Unlike the first spike in data for each year, the second spike in data is followed by relatively low data points for some time, which would make sense as this is around the November and December holiday season as students are spending this time with families and not doing work. These lower data points are not seen as much in between te first and second data spikes per year around the summer seasons, as students may be pursuing other academic endeavors such as summer classes and fellowship programs, which would prevent bookstore retail sales from dwindling significantly. It is undetermined on why the spikes in data have evolved from being higher in the fall season of each year, to being either slightly higher in the spring season or generally the same for both seasons. 

Given the non-constant seasonality present in the dataset, we investigate seasonality further by constructing seasonal plots.

## Annual Seasonality

```{r, echo=FALSE, fig.align='center', out.width='80%'}
book.seasonal = ts(df$Sales, frequency=12)

fig2 = ggseasonplot(book.seasonal) +
    ggtitle("Bookstore Retail Sales Throughout the Year") +
    xlab ("Month") + ylab ("Sales ($ millions)") +
    theme(legend.position = "none")

print(fig2)
```

The seasonal plot confirms the yearly seasonality that is present in the dataset. Data levels are extremely high in January, indicating greater visits and sales from students who are buying "back-to-school" supplies for the spring semester and quarter. The levels then drop and stay constant until July, as students have already stocked up on their school supplies and book needs for the rest of the spring season, and are taking some time off in the early summer months. Data levels then increase until peaking in August, when students are once more purchasing their school needs for the fall semester, before dropping down until October, illustrating students having bought all of their supplies once more. The data level then increase slightly until November, before spiking up in December. This increase might be because of holiday shopping. People would be buying their christmas gifts around this time, causing bookstore retail sales to jump during this season. It is interesting to see that the two peaks evident in this plot are not only occuring in January and August, as it was inferred from the qualitative description, but also occuring in December due to christmas gift shopping.

We now consider baseline models to compare to other applied models that would be appropriate for our dataset.

## Baseline Models

We now look at three simple prediction strategies:

1. **Naive:** The naive approach considers what happened in the previous period in each in-sample prediction and predicts the same thing will happen again.  
\[
\hat x_t = x_{t-1}
\]
This strategy likely isn't appropriate for the sales data since the data has seasonality and the seasonal effect appears to be relatively large. Sales in one year are more likely related to the number of sales the year earlier.However, it is best practice for analysts to use the Naive approach to utilize as a baseline to compare against more sophisticated models.

2. **Seasonal Naive** A seasonal naive strategy is the most recently observed value in each in-sample prediction in the same season. 
\[
\hat x_t = x_{t-s}
\]
In the absence of clear trend yet strong seasonality, this would be an appropriate strategy. As previously stated, sales one year are likely related to the number of sales the year prior except for exceptional cases like holidays, pandemics or periods of severe economic crises. 

3. **Constant Mean** A constant mean model is each in-sample prediction is the average of all observed data:
\[
\hat x_t = \bar x
\]
This likely will not implement well since seasonality is present. Sales on a given year are better predicted using recent numbers of sales from previous month or year, rather than an average. 

```{r,echo=FALSE, fig.align='center', out.width='65%'}
book.naive = naive(BookSales)
book.snaive = snaive(BookSales)
book.meanf = meanf(BookSales)

book.naive.RMSE = round(accuracy(book.naive)[2], 2)
book.snaive.RMSE = round(accuracy(book.snaive)[2], 2)
book.meanf.RMSE = round(accuracy(book.meanf)[2], 2)
```

The in-sample root mean squared error (RMSE) for naive, seasonal naive, and constant mean prediction methods are `r book.naive.RMSE`, `r book.snaive.RMSE`, and `r book.meanf.RMSE`.  The lowest RMSE value is for the seasonal naive method at `r book.snaive.RMSE`, which confirms our initial assumption that it is the most accurate method.  

## Decomposition Model - Classical Fit 

```{r, echo=FALSE, fig.align='center', out.width='65%'}

book.decomp = decompose(BookSales)

F_T = 1 - var(book.decomp$random, na.rm=T) / var(book.decomp$random + book.decomp$trend, na.rm=T)
F_S = 1 - var(book.decomp$random, na.rm=T) / var(book.decomp$random + book.decomp$seasonal, na.rm=T)

fig3 = autoplot(book.decomp)

print(fig3)


```

It is evident in the graphs above that there is trend and seasonality present. We also can calculate the strength of trend of the decomposition to be `r F_T` and the strength of seasonality to be `r F_S`. With the strength of seasonality being so close to 1, it is indicating that there is strong seasonality present like we assumed in the qualitative analysis. However, we can observe from the remainder that seasonality was not fully removed. There is a wave like pattern presenting itself that indicates leftover seasonality, which means that there was non-constant seasonality in our dataset. The calculated value for trend for the classical fit demonstrates a weaker trend when compared to the STL fit below.  

## Decomposition Model - STL Fitting

```{r, echo=FALSE, fig.align='center', out.width='65%'}

book.stl = stl(BookSales,s.window = 5, t.window = 9)

fig4=autoplot(book.stl)

print(fig4)

F_Ts = 1 - var(book.stl$time.series[,3], na.rm=T) / var(book.stl$time.series[,3] + book.stl$time.series[,2], na.rm=T)
F_Ss = 1 - var(book.stl$time.series[,3], na.rm=T) / var(book.stl$time.series[,3] + book.stl$time.series[,1], na.rm=T)

```

We can tell by these plots that the STL decomposition captures seasonality better than the classical fit. In looking at the graphs, we see a difference in the seasonal graph from the one generated in the classical fit.The seasonal graph in the STL fitting illustrates non-constant seasonality, and also tapers off at the end which captures how our time series plot presents the data. In addition, the STL fitting has a better axis value to capture the range of seasonality. We can also calculate the strength of trend of the decomposition to be `r F_Ts` and the strength of seasonality to be `r F_Ss`. Our calculated values for strength of trend and seasonality are different from the STL versus the classic. Both trend and seasonality are a lot higher in the STL decomposition, with both being almost 1.  In general, the STL model usually performs better with respect to unusual observations and it is more computationally intensive. This STL fit allows seasonality to change, which is therefore more accurate for our dataset. We can confirm in this decomposition that the data has strong trend and seasonality. 

## Exponential Smoothing Models 

The three exponential smoothing models include the non constant level or simple model, the Holt or double model, and the Holt-Winters or triple model. The non constant level model utilizes exponentially weighted averages of historical data to place an extra weight on recent observations. It is unsuitable for our dataset as this model is best for datasets with non constant level without trend or seasonality. The Holt model uses exponentially weighted averages of historical data as well, although it also uses them to update both level and slope. It is also unsuitable as it is best used for datasets with non-constant level, trend, and no seasonality. The Holt-Winters model uses exponentially weighted averages of historical data to update level, slope, and seasonality. It allows non-constant level, trend, and seasonality, and is hence the most suitable exponentially smoothing model. We therefore apply the Holt Winters model as the exponential smoothing model for this dataset.

```{r, echo=FALSE, fig.align='center', out.width='80%', include=FALSE}
books.hw = hw(BookSales)
summary(books.hw)
```

Looking at the smoothing parameters for the Holt-Winters model for this dataset, we can see the following values: alpha = 0.2527, beta = 0.0032, gamma = 0.7417. The value of alpha is low and closer to 1, suggesting that there is some smoothing of the level. This makes sense considering that the level is non-constant, but does not vary significantly. The beta value is similarly small, at a lesser value that is extremely close to 0, suggesting that there is little smoothing of the slope. This is understandable as albeit non-constant trend being evident, trend is not a drastic element overall, as seen by the gentle slopes in the time series plot. In contrast, the gamma value is large and closer to 1, suggesting that there is significant smoothing of seasonality. This once again makes sense, considering the extreme drastic levels of non-constant seasonality that is present in the dataset.

```{r, echo=FALSE, fig.align='center', out.width='80%'}
fig5 = autoplot(BookSales) + autolayer(fitted(books.hw), series="HW") + ggtitle("Holt Winters Plot for Monthly Bookstore Sales") + xlab("Year") + ylab("Sales ($ millions)") + theme(plot.title = element_text(hjust = 0.5))
print(fig5)

fig6 = autoplot(resid(books.hw)) + ggtitle("Holt Winters Residuals Plot") + xlab("Year") + ylab("Residuals") + theme(plot.title = element_text(hjust = 0.5))
print(fig6)
fig7 = ggAcf(resid(books.hw)) + ggtitle("Holt Winters ACF Plot") + xlab("Year") + ylab("ACF") + theme(plot.title = element_text(hjust = 0.5))
print(fig7)
```

The Holt-Winters model has a relatively good fit with the dataset, with an RMSE value of 87.71564 that i relatively low considering the high values in the dataset. This is also seen in how the generated Holt-Winters plot matches up extremely well with the time series plot, illustrating that at first glance, this model is an excellent fit for exponential smoothing. The only sections in which the Holt-Winters plot differs slightly from the original time series plot is the start and the outlier in 2020. The Holt-Winters plot has greater data fluctuations in around 1992 and 1993, as well as in 2020. The good model fit is supported in the first residual plots, which demonstrates Gaussian white noise and a relatively stationary plot. However, there are certain points in this plot that varies significantly, with residuals of -400 around 1993, 2012, and 2020 (although this was an indicated outlier). The correlogram demonstrating ACF values has slightly different results. This plot does not illustrate clear white noise and also illustrates evidence of slight autocorrelation at lag 1 of close to 0.125 and of strong autocorrelation at lag 10 of close to -0.2. This indicates that model assumptions are violated and that prediction intervals are less trustworthy, which calls into question any coefficients that were barely statistically sig would be called into question.

We now consider the SARIMA family of models to remove the autocorrelation present in the residuals.

## SARIMA Family of Models 
### SARIMA Model I (Investigation)
The SARIMA family of models is a great option when dealing with time series that have non-constant level, changing trend, and seasonality. As a first step, an initial fitting algorithm will be ran in R - this algorithm selects orders of differencing to make the data stationary, then selects autoregressive and moving average values based on criteria such as AIC. This algorithm will give an initial recommendation on what SARIMA combination to use and then we'll tweak the parameters to try to improve the model. 

```{r, echo=FALSE, include = FALSE}
BookSales.autoarima = auto.arima(BookSales)

```
```{r, echo=FALSE}
BookSales.autoarima
```

The initial model is ARIMA(1,1,1)(0,1,1)[12]. This means that:

ARIMA(p,d,q)(P,D,Q)[s] where:
p = autoregressive terms for the time series |
d = order of differencing to make the data stationary |
q = moving average terms for the time series errors |
P = autoregressive terms for seasonality |
D = order of differencing to account for seasonality and make it stationary |
Q = moving average terms for the seasonality errors |
[s] = frequency of the seasonality.

What the initial model is telling us is that it is taking a first order difference of the time series and the seasonality to make the data stationary. After that, it applies one autoregressive term for the data itself and none for the seasonality component. Also, it applies a moving average model on the errors with one moving average term for the time series while also applying the same amount for the seasonality. In this time series, the seasonality is taken into account every 12 months.

Now, let's dig further to determine if these terms are statistically significant:

```{r, echo=FALSE}
confint(BookSales.autoarima)
```

As we can tell by the confidence intervals, the autoregressive term for the time series (ar1) and both of the moving average components (ma1 & sma1) are statistically significant since 0 is not present in their significance range.

```{r, echo=FALSE, fig.align='center', warning=FALSE,  message=FALSE}
fig8 = autoplot(resid(BookSales.autoarima)) + ggtitle("SARIMA Model I Residuals") + ylab("Residuals") +
  xlab("Year")+theme(plot.title = element_text(hjust = 0.5)) 
print(fig8)
```

By analyzing the residuals plot for SARIMA Model I, we can determine that the residuals look stationary with the mean centered around zero and somewhat constant variance except for outliers with extreme values in the years of 2002, 2012, 2020, and 2021.

```{r, echo=FALSE, fig.align='center'}
fig9 = ggAcf(resid(BookSales.autoarima)) + ggtitle("ACF for SARIMA Model I") + theme(plot.title = element_text(hjust = 0.5)) 
print(fig9)
```

The correlogram for the residuals of this model seems to exhibit positive autocorrelation at lag 5 and negative autocorrelation at lags 10, 13, and 14.

```{r, echo=FALSE, include=FALSE}
accuracy(BookSales.autoarima)
```

Overall, this initial model seems like a good starting point since the autoregressive and moving average terms were statistically significant. Furthermore, the residuals do demonstrate stationarity but with some levels of autocorrelation still present. The accuracy Root Mean Squared Error (RMSE) for this model has a value of 80.78. We will attempt to improve this model by looking into other SARIMA models in this section.

### SARIMA Model II
For this model, we will test a ARIMA(1,1,1)(1,1,1)[12]. In here, we are increasing the autoregressive term for the seasonal component by one.

```{r, echo = FALSE, include=FALSE}
BookSales.SARIMA.II = arima(BookSales, order = c(1, 1, 1), seasonal = list(order = c(1,1,1)), include.mean = FALSE)
```

```{r, echo=FALSE}
BookSales.SARIMA.II
```

These are the coefficients for the SARIMA Model II. Below we will test for their significance:

```{r, echo=FALSE}
confint(BookSales.SARIMA.II)
```

```{r,echo=FALSE, include=FALSE}
accuracy(BookSales.SARIMA.II)
```

By testing for significance, we can determine that adding the seasonal autoregressive term (sar1) is not significant and should not be included. We will not display the graph of residuals or correlogram for to avoid redundancy as it is similar to the SARIMA I model. We did get a lower RMSE value of 80.58 for this model (technically showing a slightly improved in-sample accuracy), but the insignificant seasonal autoregressive term makes this accuracy measure untrustworthy.

**Most Successful Model of the SARIMA Family of Models:** Our investigation of the SARIMA Family of Models has led us to conclude that the most successful model was the SARIMA Model I: SARIMA(1,1,1)(0,1,1)[12] with an in-sample accuracy RMSE of 80.78. The fitted SARIMA model on the time series is graphed below.

```{r, echo=FALSE, fig.align='center', warning=FALSE, message=FALSE}
fig10 = autoplot(BookSales) + ggtitle("Us Monthly Bookstore Sales 1992-2022") + ylab("Sales ($ millions)") + theme(plot.title = element_text(hjust = 0.5)) + autolayer(fitted(BookSales.autoarima), series = "SARIMA I Model")+ xlab("Year")
print(fig10) 
```

## Linear Regression 

Linear models for time series have the ability to include both trend and seasonality in its calculations. Since our time series data seems to exhibit a quadratic shape, we will transform the trend to include a quadratic term in the regression.

```{r, echo=FALSE, include=FALSE}
BookSales.lm = tslm(BookSales~poly(trend,2) + season)
summary(BookSales.lm)
accuracy(BookSales.lm)
```

The fitted linear model can be described using the following equation:

\[
BookSales = 1,555.38-1,501.30trend-4,358.98trend^2- 734.46S_2 - 755.69S_3 - 791.19S_4 - 685.81S_5 -691.71S_6- 708.89S_7 + 45.20S_8
\]

\[
-369.18S_9 - 720.77S_{10} - 681.04S_{11} + 38.01S_{12}
\]

In this model, S2-S12 represent the seasonal effect for the months of February - December (January is the base case). All of the variables are significant at the 99% confidence level except for the months of August (S8) and December (S12). Of all the months, April shows the least amount of sales with a value of $791 million less than in January. On the other hand, the highest amount of sales are during the month of August and December having \$452,000 and \$380,000 more in sales than January respectively. However, as mentioned before, these coefficients are not statistically significant but could be because of the high volatility that the data experiences during those periods. The multiple R-squared value for this model is 0.8543, which means it can explain 85.43% of the variations in book sales given the variations of the time series' trend and seasonality. Finally, the in-sample accuracy RMSE exhibits a value of 165.88.

```{r, echo=FALSE, fig.align='center', warning=FALSE, message=FALSE}
fig11 = autoplot(resid(BookSales.lm)) + ggtitle("Linear Regression Residuals") + ylab("Residuals") +
  xlab("Year")+theme(plot.title = element_text(hjust = 0.5)) 
print(fig11)

```

By analyzing the residuals, we see that they are somewhat stationary and variation seems relatively constant. However, there still seems to exist some varying trend and non-constant level affecting the residuals given that they don't seem to be centered around mean zero. Below we will proceed to analyze the residuals' autocorrelation.

```{r, echo=FALSE, fig.align='center'}
fig12 = ggAcf(resid(BookSales.lm)) + ggtitle("ACF for Linear Model") + theme(plot.title = element_text(hjust = 0.5)) 
print(fig12)

```

The correlogram demonstrates that there are considerable amounts of autocorrelation which means that the independence assumption of linear regression is violated and the significance of the terms are not reliable. However, we can fit a SARIMA model on the residuals to be able to make corrections to the initial model.

### SARIMA Model on Residuals
The SARIMA model that will be fit on the residuals is ARIMA(3,0,3)(0,1,1)[12]. We are taking one seasonal differencing to make the residuals stationary and one moving average seasonal term. Furthermore, we are applying three autoregressive and three moving average terms to the residuals time series.

```{r, echo=FALSE, include=FALSE}
BookSales.lm.resid = resid(BookSales.lm)

BookSales.lm.resid.SARIMA = auto.arima(BookSales.lm.resid)

confint(BookSales.lm.resid.SARIMA) # ar4 not significant so taking it out

BookSales.lm.resid.SARIMAII = arima(BookSales.lm.resid, order = c(3, 0, 3), seasonal = list(order = c(0,1,1)), include.mean = FALSE )

confint(BookSales.lm.resid.SARIMAII)
```

```{r,echo=FALSE}
confint(BookSales.lm.resid.SARIMAII)
```

The confidence intervals of the SARIMA model on the residuals shows that all of the terms are within the significance range.


```{r, echo=FALSE, fig.align='center', warning=FALSE, message=FALSE}

fig13 = autoplot(resid(BookSales.lm.resid.SARIMAII)) + ggtitle("Residuals for SARIMA Model on Linear Regression Residuals") + ylab("Residuals") +
  xlab("Year")+theme(plot.title = element_text(hjust = 0.5))
print(fig13)
```

As we can see, the residuals plot has greatly improved by having the residuals centered around mean zero. Now, we can check if the autocorrelation has been fixed.


```{r, echo=FALSE, fig.align="center"}
fig14 = ggAcf(resid(BookSales.lm.resid.SARIMAII)) + ggtitle("ACF for SARIMA Model Residuals on Linear Model") + theme(plot.title = element_text(hjust = 0.5)) 
print(fig14)

```

We can see that modeling the linear regression's residuals with a SARIMA model significantly improved the autocorrelation, having the ACF measures contained within the significance range.

### Linear Model with SARIMA for Residuals
As discussed in this section, we have determined that fitting an ARIMA (3,0,3)(0,1,1)[12] model on the linear model's residuals is successful and significantly improved the strength and reliability of the model. Even when comparing in-sample accuracies, the linear model went from an RMSE of 165.88 to 76.65, an improvement of 53.79%.

```{r, echo=FALSE, include = FALSE}
fitted.complete.test =  fitted(BookSales.lm) + fitted(BookSales.lm.resid.SARIMAII)

accuracy(BookSales.lm)
accuracy(fitted.complete.test, BookSales) #76.58
```
The corrected linear model is graphed below.


```{r, echo=FALSE, fig.align='center', warning=FALSE, message=FALSE}
fig15 = autoplot(BookSales) + ggtitle("US Monthly Bookstore Sales 1992-2022") + ylab("Sales ($ millions)") + theme(plot.title = element_text(hjust = 0.5)) + autolayer(fitted.complete.test, series = "LM + SARIMA") + xlab("Year")

print(fig15)
```

## Extra Topic: Linear Regression with Box Cox Transformation

We will now consider a Box Cox transformation to address non-constant variance in our dataset, which we will apply to consequent model fittings. We will follow the same type of model used in the linear regression section by including a quadratic term for the trend and having seasonality as dummy variables.

The Box Cox transformation converts non-normal data into a normal distribution, improving the accuracy of predictions made using linear regression. It might therefore be a good statistical technique for datasets with non-constant variance. Given that our data exhibits some of this quality, the Box Cox transformation could be a good tool to utilize.

```{r, echo=FALSE, fig.align='center', out.width='80%'}

boxcox = BoxCox(BookSales, lambda="auto")
fig16 = autoplot(boxcox) + xlab('Year') + ylab('Variance Factor') + ggtitle("Box Cox Plot")

print(fig16)
```

The following Box Cox plot illustrates a flatter curve with smaller annual data fluctuations, due to the non-constant variance that has been removed. We apply this transformation onto our linear regression as an extra factor to potentially increases model fit and in-sample accuracy. 

```{r, echo=FALSE, fig.align='center', out.width='80%'}

book.boxcox = tslm(BookSales~poly(trend,2) + season, lambda = "auto")
fig17 = autoplot(resid(book.boxcox)) + xlab('Year') + ylab('Residuals') + ggtitle("Residuals Linear Regression with Box Cox Transformation") + theme(plot.title = element_text(hjust = 0.5))

print(fig17)

```

```{r, echo=FALSE, include=FALSE}
summary(book.boxcox)
test.em = auto.arima(resid(book.boxcox))
complete = fitted(book.boxcox) + fitted(test.em)
accuracy(complete, BookSales)
```

```{r, echo=FALSE, fig.align='center', out.width='80%'}
fig18 = ggAcf(resid(book.boxcox)) + ggtitle("ACF for SARIMA Model Residuals on Linear Model with Box Cox") + theme(plot.title = element_text(hjust = 0.5)) 

print(fig18)
```
The linear regression with Box-Cox transformation illustrates a flatter curve with more controlled variance and smaller annual data fluctuations, due to the non-constant variance that has been removed. All of the variables seem to be significant except for the seasonal dummy terms for the months of August and December. Also, it has Multiple R-squared value of 0.8735 which means this model can explain 87.35% of the variations in the response variable given changes in the explanatory variables.

However, by looking at the residuals and correlogram, it still shows significant autocorrelation and might need to conduct a quick SARIMA Model on the residuals.

```{r, echo=FALSE,  fig.align='center', out.width='80%'}
fig19 = autoplot(BookSales) + autolayer(complete, series="LM_Box Cox + SARIMA") + xlab('Year') + ylab('Sales ($ millions)') + ggtitle("US Monthly Bookstore Sales 1992-2022") + theme(plot.title = element_text(hjust = 0.5))

print(fig19)
```

After determining an ARIMA(1,0,2)(1,0,2)[12] model on the residuals and applying the corrections to the linear regression model, we get an RMSE of 127.89. Overall, the in-sample predictions for the Box-Cox linear regression model are not as good when compared to our previous linear regression model (with an RMSE of 76.58). This could be due to the fact that by looking at the plots, we can see that the Box-Cox transformation is missing some of the volatility in the actual time series.

We now move on to exploring our last section of models, which is non-linear regression.

## Non-linear Regression 

For this section, we apply the quadratic formula onto our dataset, as this formula has an "upside down U" shape that is similar to our time series plot. We had considered looking into the Bass model, a model for product lifecycle introduced by Frank Bass which is useful for estimating future sales, market sizes, and product lifetimes. The model considers two types of customers, which are the innovators who purchase products based on product information and advertisements, and the imitators who purchase products based on others' experiences and product usage. As our dataset considers bookstore retail sales, this consideration of the two customer types therefore does not apply to this situation, which is why we decided against plotting the Bass model despite how its plot is also an "upside down U" shape.

```{r, echo=FALSE, fig.align='center', out.width='80%'}

t = 1:length(BookSales)
book.qd = nls(BookSales ~ (a*(t-172)^2 + b*t + c + 2000), start = list(a=1, b=1, c=1))
print(book.qd) 

book.qdfitted = ts(fitted(book.qd), start=1992, frequency = 12)

fig20 = autoplot(BookSales, series = 'Time Series') + autolayer(book.qdfitted, series = 'Quadratic Formula') + xlab('Year') + ylab('Sales ($ millions)') + ggtitle("Monthly Bookstore Retail Sales 1992-2022 with Quadratic Formula Fitting")

print(fig20)
```

The quadratic formula plot does not fit well against our original time series plot. Although it captures the general change of the data level, it underestimates the data and removes the annual data fluctuations that presents an important quality in the time series plot. In addition, it asserts that the bookstore retail sales would increase at an increasing rate before decreasing at a decreasing rate. Furthermore, this quadratic equation's range is from negative infinity up until ~$1.25 billion - so in terms of predictive power it will not be useful because after the function reaches the high point at the vertex, it will decrease constantly towards negative infinity (which is not possible for book sales). Overall, this model is not a great fit onto our dataset. 

## Comparison of In-Sample Accuracies and Model Recommendation

```{r, echo=FALSE}
hw.RMSE = round(accuracy(books.hw)[2], 2)
arima.RMSE = round(accuracy(BookSales.autoarima)[2], 2)
sarima.RMSE = round(accuracy(BookSales.SARIMA.II)[2], 2)
lr.RMSE = round(accuracy(BookSales.lm)[2], 2)
lrsarima.RMSE = round(accuracy(fitted.complete.test, BookSales)[2], 2)
lrsarimabc.RMSE = round(accuracy(complete, BookSales)[2], 2)
```

Seasonal Naive: `r book.naive.RMSE`, Holt Winters: `r hw.RMSE`
ARIMA: `r arima.RMSE`, SARIMA: `r sarima.RMSE`,
Linear Regression: (normal) `r lr.RMSE`, (with SARIMA on residuals) `r lrsarima.RMSE`, (with Box Cox Transformation and SARIMA on residuals) `r lrsarimabc.RMSE`

In comparing the RMSE values of all of the successful and "good-fit" models we investigated, we created the following ascending order of models from the lowest RMSE value (most accurate) to the highest RMSE value (least accurate): 

Linear Regression with SARIMA on residuals < SARIMA < ARIMA < Holt Winters < Linear Regression with Box Cox & SARIMA on Residuals < Linear Regression < Seasonal Naive

In comparing the RMSE values of all of the successful and "good-fit" models we investigated, the linear regression model that applied SARIMA on its residuals had the lowest RMSE value by far of 76.65521. It is the most accurate model for this dataset that we have covered in our MA611 Time Series class and is the model that we would recommend using to create in-sample predictions and forecasts. 

## Citations

Atwell, A. (2023, March 15). E-book. Encyclopædia Britannica. Retrieved from https://www.britannica.com/technology/e-book 

Cherveny, L. (2023). *MA611: Time Series Analysis Spring 2023 Class Slides*. Retrieved from http://lukecherveny.com/ma611spring23/

National Archives and Records Administration. (n.d.). Brief on Educational Progress 1992-2000. National Archives and Records Administration. Retrieved from https://clintonwhitehouse4.archives.gov/WH/New/html/edprogress_report.html 

Talbot, Dean. (2022, December 20). Used Book Sales Statistics. BooksRated. Retrieved from https://wordsrated.com/used-books-statistics/#:~:text=As%20of%202022%2C%20the%20market,of%205.5%25%20from%20%2422.78%20billion.
